Evaluating a simplified forecast model in comparison to the European forecasting hub ensemble

### 2022-09-27 paper/paper.Rmd
fix caption

```{r vis-forecasts, fig.cap = a.) Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one and four weeks). 30\\%, 60\\%, and 90\\% prediction intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time.
b.) A replicate of a.) but with incidence rates on the log scale. c.) Weighted interval scores at the one-week and four-week forecast horizon by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom on the log scale.", out.width = "95%", fig.height = 12, fig.width = 18}
p <- (
  plot_forecast_custom(forecasts, log = FALSE) |
  plot_forecast_custom(forecasts, log = TRUE) +
  labs(y = "") |
  plot_wis(wis, locs)
) +
  plot_layout(widths = c(2, 2, 1), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
suppressWarnings(print(p))
```

>>>>

```{r vis-forecasts, fig.cap = "a.) Forecasts of notified test positive cases (per 10,000 population) by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom,  by forecast horizon (one and four weeks). 30\\%, 60\\%, and 90\\% prediction intervals are shown. The black line and points are the notified cases as of the date of data extraction rather than those available at the time. b.) A replicate of a.) but with incidence rates on the log scale. c.) Weighted interval scores at the one-week and four-week forecast horizon by epidemiological week in Germany, Greece, Italy, Poland, Slovakia, and the United Kingdom on the log scale.", out.width = "95%", fig.height = 12, fig.width = 18}
p <- (
  plot_forecast_custom(forecasts, log = FALSE) |
  plot_forecast_custom(forecasts, log = TRUE) +
  labs(y = "") |
  plot_wis(wis, locs)
) +
  plot_layout(widths = c(2, 2, 1), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
suppressWarnings(print(p))
```
